Cover letter for ``Two applications\dots''

### 2021-03-06 papers/types2020/revisions/sec3.tex
Fixing merge.

Figure~\ref{fig:augmented} contains an annotated version of these
proof rules: the annotations help us connect to elements of the Coq
proof system.
\begin{enumerate}
  \item Instead of having separate connectives for $\forall$ and
    $\supset$, we have the dependent product connective $(x:A)D$. 
  \item We account for \emph{computation} inside atoms by generalizing
    the \emph{init} rule to allow for term-level conversion.
  \item We have incorporated both \emph{proof
  certificates}~\cite{chihani17jar} (using the schematic variable
    $\XXi$) along with expert predicates (predicates with the $e$
    subscript). We explain these in Section~\ref{ssec:cert}.
  \item The inference rules are  annotated by terms structures that
    can be given directly to the Coq kernel for checking.
  \item We have added various premises which are responsible for
    pulling information from Coq's global environment.
\end{enumerate}
The proof system described in Figure~\ref{fig:augmented} (and
implemented in Figure~\ref{fig:kernel}) corresponds to a subset of the Calculus
of Inductive Constructions in which inductive definitions are
limited to % first-order
Horn clauses.
%
This  system is inspired by the calculus for proof search in
Pure Type Systems introduced in \cite{LengrandDM06}, based in turn on
ideas stemming from focusing (in particular, the LJT calculus of
Herbelin \cite{Herbelin94}). Similar to that calculus, we have a
term language that includes terms and lists of terms, and two distinct
typing judgments for the two categories.
% %
% In our case, the \lP goal formula \lsti{(check Xi (go B T))}
% corresponds to $\XXi\vdash B \colon T$ and the formula
% %
% \lsti{(check Xi (bc D B L))} corresponds to $\XXi\Downarrow L\colon
% D\vdash B$.
%
This style of  proof terms coincides with the idea behind the \emph{spine
  calculus}~\cite{Cervesato97tr}.  The main novelty of our proof
system here is that proof terms and proof certificates are used
simultaneously in all inference rules.

The proof system is parameterized by Coq's global environment $E$,
here a set of constant and inductive definitions; following Coq's
reference manual, inductive definition are denoted by
$\mathrm{Ind}[p] (\Gamma_I := \Gamma_C)$, where $\Gamma_I$ determines
the names and types of the (possibly mutually) inductive type and
$\Gamma_C$ the names and types of its constructors; finally $p$
denotes the number of parameters and plays here no role. We delegate to
Coq's type checking the enforcement of the well-sortedness of
inductive types. The \emph{local context} is empty, since we are only
dealing with types that correspond to Horn clauses, and atomic types
are inductively defined. In fact, we do not have a $\forall$ rule on
the right, although the proof theory would gladly allow it. This means
at the term level that there are no variables in our grammar of
terms. Terms are always applied to a (possibly empty) list of
arguments.  The \emph{decide} rule, % is the equivalent in our
% a \emph{decide} rule in an explicitly focused system
% \cite{liang09tcs}.  
as in the previous proof system for Horn logic,  given an atom,
 selects a clause on which to backchain on: we lookup the
constructors of an inductive definition from the global
environment, one that matches the head symbol of the atom we aim to backchain on, and then
call the latter judgment that will find a correct instantiation, if any. The rules for backchaining include
 the (conflation of the) left introduction rules for
$\forall$ and $\supset$, as well as the \emph{init} rule, which incorporates Coq's conversion.

@@

\newpage
\subsubsection{FPC-specific code}
\label{ssec:fpc}

@@

***

@@

\newpage

>>>>

Figure~\ref{fig:augmented} contains an annotated version of these
proof rules: the annotations help us connect to elements of the Coq
proof system.
\begin{enumerate}
  \item Instead of having separate connectives for $\forall$ and
    $\supset$, we have the dependent product connective $(x:A)D$. 
  \item We account for \emph{computation} inside atoms by generalizing
    the \emph{init} rule to allow type-level conversion.
  \item We have incorporated  \emph{proof
  certificates}~\cite{chihani17jar} (using the schematic variable
    $\XXi$) along with \emph{expert predicates} (predicates with the $e$
    subscript). We explain these in Section~\ref{ssec:cert}.
  \item The inference rules are  annotated by terms structures that
    can be given directly to the Coq kernel for checking.
  \item We have added various premises which are responsible for
    interacting with Coq.
\end{enumerate}
The proof system described in Figure~\ref{fig:augmented} (and
implemented in Figure~\ref{fig:kernel}) corresponds to a subset of the Calculus
of Inductive Constructions in which inductive definitions are
limited to % first-order
Horn clauses.
%
This  system is inspired by the calculus for proof search in
Pure Type Systems introduced in \cite{LengrandDM06}, based in turn on
ideas stemming from focusing (in particular, the LJT calculus of
Herbelin \cite{Herbelin94}). Similar to that calculus, we have a
term language that includes terms and lists of terms, and two %distinct
typing judgments for the two categories.
% %
% In our case, the \lP goal formula \lsti{(check Xi (go B T))}
% corresponds to $\XXi\vdash B \colon T$ and the formula
% %
% \lsti{(check Xi (bc D B L))} corresponds to $\XXi\Downarrow L\colon
% D\vdash B$.
%
This style of  proof terms coincides with the idea behind the \emph{spine
  calculus}~\cite{Cervesato97tr}.  The main novelty of our proof
system here is that proof terms and proof certificates are used
simultaneously in all inference rules.

The proof system is parameterized by Coq's global environment $E$,
here a set of constant and inductive definitions; following Coq's
reference manual, inductive definition are denoted by
$\mathrm{Ind}[p] (\Gamma_I := \Gamma_C)$, where $\Gamma_I$ determines
the names and types of the (possibly mutually) inductive type and
$\Gamma_C$ the names and types of its constructors; finally $p$
denotes the number of parameters and plays here no role. The {local context} is empty, since we are only
dealing with types that correspond to Horn clauses, and atomic types
are inductively defined. In fact, we do not have a $\forall$ rule on
the right, although the proof theory would gladly allow it. This means
that there are no variables in our grammar of
terms. Terms are always applied to a (possibly empty) list of
arguments.   We delegate to
Coq's type checking the enforcement of the well-sortedness of
inductive types.  The {decide} rule, % is the equivalent in our
% a \emph{decide} rule in an explicitly focused system
% \cite{liang09tcs}.  
as in the previous proof system for Horn logic,  given an atom,
 selects a clause on which to backchain on: we lookup the
constructors of an inductive definition from the global
environment, one that matches the head symbol of the atom we aim to backchain on, and then
call the latter judgment that will find a correct instantiation, if any. The rules for backchaining include
 the (conflation of the) left introduction rules for
$\forall$ and $\supset$, as well as the \emph{init} rule, which incorporates Coq's conversion.

@@

%\newpage
\subsubsection{FPC-specific code}
\label{ssec:fpc}

@@

*** DM Continue here

@@

%\newpage
